### 2022-11-04 paper.Rmd
ESEM rectified

#Rename variables
names(esem_data) <- paste0("x", c(1:29))

@@

rel.esm <- reliability(esem_fit, return.total = TRUE)

rel.esm.m <- rel.esm[4,]

@@

rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)

rel.esm_ho.m <- rel.esm_ho[4,]

>>>>

#Rename variables
# names(esem_data) <- paste0("x", c(1:29))

@@

rel.esm <- reliability(esem_fit, return.total = TRUE)
# 
# rel.esm.m <- rel.esm[4,]

esemComp::omega_esem(esem_fit,target_rot )

@@

# rel.esm_ho <- reliability(esem_fit_higher_order , return.total = TRUE)
# 
# rel.esm_ho.m <- rel.esm_ho[4,]
